---
title: "AdvNumEng_TP_WANG Andi"
author:WANG Andi
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Preliminary sampling of model
0. Build a first design of experiments based on 100 random simulations. Plot.
??? scatter plot: pairs(), pairsD3::pairsD3()
??? parallel coordinates plot: MASS::parcoord(), parcoords::parcoords() or plotly::plot_ly

we can build each column of the design with random number, so we have:
```{r cars}
x<-runif(100,0,1)
y<-runif(100,0,1)
z<-runif(100,0,1)
a<-runif(100,0,1)
p<-runif(100,0,1)
mat<-cbind(x,y,z,a,p)
colnames(mat)<-c("x","y","z","a","p")
wls<-compute_wls(mat)
```

then we plot the matrix:
```{r mat,echo=FALSE}
pairs(cbind(mat,wls))
```

```{r mat,echo=FALSE}
library(pairsD3)
pairsD3(cbind(mat,wls))
```

```{r mat,echo=FALSE}
library(MASS)
parcoord(cbind(mat,wls))
```


if we use the seq for getting the variables a and p we have the result:
```{r cars}
xx<-runif(100,0,1)
yy<-runif(100,0,1)
zz<-runif(100,0,1)
aapp<-expand.grid(seq(0,1,length=10), seq(0,1,length=10))
mat1<-cbind(x,y,z,aapp)
colnames(mat1)<-c("x","y","z","a","p")
wls1<-compute_wls(mat1)
```

then we plot the matrix:
```{r mat1,echo=FALSE}
pairs(cbind(mat1,wls1))
```

```{r mat1,echo=FALSE}
library(pairsD3)
pairsD3(cbind(mat1,wls1))
```

```{r mat1,echo=FALSE}
library(MASS)
parcoord(cbind(mat1,wls1))
```

Magma chamber optimization
1. Perform an optimization of the magma chamber to find a first calibrated magma chamber (wls < ???1.5)
Full identification of magma chamber

for this question we need to use the model EGO which we have used in the class, so that we have the code:

```{r cars}
source("mainScript_DatascienceClass.R")
library(DiceOptim)
set.seed(123)

# a 9-points factorial design, and the corresponding response
d <- 5
n <- 100
x1<-runif(100,0,1)
x2<-runif(100,0,1)
x3<-runif(100,0,1)
design.fact <- cbind(x1,x2,x3,expand.grid(seq(0,1,length=10), seq(0,1,length=10)))

design.fact <- data.frame(design.fact)
names(design.fact)<-c("x", "y","z","a","p")
response.branin <- data.frame(apply(design.fact, 1, compute_wls))
names(response.branin) <- "y"

# model identification
fitted.model1 <- km(~1, design=design.fact, response=response.branin,
                    covtype="matern5_2", control=list(pop.size=50,trace=FALSE), parinit=c(0.5, 0.5))

### EGO##################
library(rgenoud)
nsteps <- 100
lower <- rep(0,d)
upper <- rep(1,d)
oEGO <- EGO.nsteps(model=fitted.model1, fun=compute_wls, nsteps=nsteps,
                   lower=lower, upper=upper, control=list(pop.size=20, BFGSburnin=2))
print(oEGO$par)
print(oEGO$value)

```
we can get 100 points when we set the nsteps=100, we find the point in these result of which the value of y< -1.5

```{r cars}
matwls<-oEGO$value
matpt<-oEGO$par

index<-(which(matwls< -1.5))

matopt<-matpt[index,]
matopt
```

plot the entire optimization model:
```{r wls,echo=FALSE}
op<-par(mfrow=c(2,3))
plot(matpt[,1],matwls-mean(matwls))

lines(smooth.spline(matpt[,1],matwls-mean(matwls)),col='red')
plot(matpt[,2],matwls-mean(matwls))
lines(smooth.spline(matpt[,2],matwls-mean(matwls)),col='red')
plot(matpt[,3],matwls-mean(matwls))
lines(smooth.spline(matpt[,3],matwls-mean(matwls)),col='red')
plot(matpt[,4],matwls-mean(matwls))
lines(smooth.spline(matpt[,4],matwls-mean(matwls)),col='red')
plot(matpt[,5],matwls-mean(matwls2))
lines(smooth.spline(matpt[,5],matwls-mean(matwls)),col='red')
par(op)

```

2. Based on previous design, build a meta-model and plot it. Propose a target level for inversion (considering previous optimization results)

```{r cars}
mat2<-expand.grid(matopt[,1],matopt[,2],matopt[,3],matopt[,4],matopt[,5])
matwls2<-compute_wls(mat2)

```
```{r cars}
matwls2
min(matwls2)
```
```{r wls,echo=FALSE}
op<-par(mfrow=c(2,3))
plot(mat2[,1],matwls2-mean(matwls2))

lines(smooth.spline(mat2[,1],matwls2-mean(matwls2)),col='red')
plot(mat2[,2],matwls2-mean(matwls2))
lines(smooth.spline(mat2[,2],matwls2-mean(matwls2)),col='red')
plot(mat2[,3],matwls2-mean(matwls2))
lines(smooth.spline(mat2[,3],matwls2-mean(matwls2)),col='red')
plot(mat2[,4],matwls2-mean(matwls2))
lines(smooth.spline(mat2[,4],matwls2-mean(matwls2)),col='red')
plot(mat2[,5],matwls2-mean(matwls2))
lines(smooth.spline(mat2[,5],matwls2-mean(matwls2)),col='red')
par(op)

```
in this question, we need to find a value for T which is the level for inversion, by the results that we got from the prior question, we choose wls<-2.645 for inversion.


3. Using Bichon criterion (from KrigInv package), propose next simulation. Iterate. Plot.
```{r cars}
library(KrigInv)
set.seed(123)
lower <- rep(0,d)
upper <- rep(1,d)
mbichon<-max_infill_criterion(lower=lower, upper=upper,method = "bichon",T=-2.64519,model=fitted.model1)

```
```{r cars}
mbichon$par
mat3<-cbind(runif(1000,0,1),runif(1000,0,1),runif(1000,0,1),runif(1000,0,1),runif(1000,0,1))

mat3<-as.matrix(mat3)

```
```{r bichon,echo=FALSE}

```
4. Using SUR criterion (from KrigInv package), propose next simulation. Iterate by batch (size=10).Plot.
```{r cars}
set.seed(123)
lower <- rep(0,d)
upper <- rep(1,d)
msur<-max_sur(lower, upper, optimcontrol = NULL, 
integration.param = NULL, T=-2.64519, model=fitted.model1, 
new.noise.var = 0, real.volume.variance = FALSE, real.volume.constant = FALSE)
```
```{r cars}
msur$par
mat4<-cbind(runif(1000,0,1),runif(1000,0,1),runif(1000,0,1),runif(1000,0,1),runif(1000,0,1))

mat4<-as.matrix(mat4)

```
```{r bichon,echo=FALSE}


```
5. Compare and analyse results of 3. & 4.

when we observe the images and the results gotten from question 4 and question 3, we can find that there are great difference of the effet of each variable.
for the question 3 we can find that x, y, p is more important to the wls, and for the question 5, we will see that y,z are more important.
